Analyzing X-ray images in Python with scikit-image

### 2016-08-22 skimage_tomo.tex
Wait for end of proposition to cite

The acquisition time of synchrotron tomography images has decreased
dramatically over the last decade, from hours to
seconds \citep{Maire2014}. New modalities such as single-bunch
imaging \citep{Rack2014} provide a time resolution down to the nanosecond
for radiography. However, the time subsequently spent in processing the
images has not decreased as much, so that the outcome of a successful
synchrotron imaging run often takes weeks or even months to be
transformed into scientific results.

@@

\texttt{scikit-image} offers a wide variety of image processing
algorithms, using a simple interface natively compatible with 2D and 3D
images. It is well integrated into the Scientific Python ecosystem, so
that it interfaces well with visualization libraries and other data
processing packages. \texttt{scikit-image} has seen tremendous growth
since its creation in 2009, both in terms of users and proposed features.
In addition to the growing number of scientific teams that use
\texttt{scikit-image} for processing images of various X-ray modalities,
domain-specific tools are now using \texttt{scikit-image} as a dependency
to build upon. Examples include \texttt{tomopy} \citep{Gursoy2014} for
tomographic reconstruction, or \texttt{DIOPTAS} \citep{Prescher2015} for
the reduction and exploration of X-ray diffraction data. It is likely
that more application-specific software will benefit from depending on
\texttt{scikit-image} in the future, since \texttt{scikit-image} strives
to be domain-agnostic and to keep the function interface stable. On the end-user
side, future work includes better integration of parallel processing
capabilities, completion of full 3-D compatibility, an enriched narrative
documentation, speed enhancements, and expansion of the set of supported algorithms.

>>>>

The acquisition time of synchrotron tomography images has decreased
dramatically over the last decade, from hours to
seconds \citep{Maire2014}. New modalities such as single-bunch
imaging provide a time resolution down to the nanosecond
for radiography \citep{Rack2014}. However, the time subsequently spent in processing the
images has not decreased as much, so that the outcome of a successful
synchrotron imaging run often takes weeks or even months to be
transformed into scientific results.

@@

\texttt{scikit-image} offers a wide variety of image processing
algorithms, using a simple interface natively compatible with 2D and 3D
images. It is well integrated into the Scientific Python ecosystem, so
that it interfaces well with visualization libraries and other data
processing packages. \texttt{scikit-image} has seen tremendous growth
since its creation in 2009, both in terms of users and included features.
In addition to the growing number of scientific teams that use
\texttt{scikit-image} for processing images of various X-ray modalities,
domain-specific tools are now using \texttt{scikit-image} as a dependency
to build upon. Examples include \texttt{tomopy} \citep{Gursoy2014} for
tomographic reconstruction, or \texttt{DIOPTAS} \citep{Prescher2015} for
the reduction and exploration of X-ray diffraction data. It is likely
that more application-specific software will benefit from depending on
\texttt{scikit-image} in the future, since \texttt{scikit-image} strives
to be domain-agnostic and to keep the function interface stable. On the end-user
side, future work includes better integration of parallel processing
capabilities, completion of full 3-D compatibility, an enriched narrative
documentation, speed enhancements, and expansion of the set of supported algorithms.
